Modified replication

### 2020-11-09 rep_nosmooth/README.Rmd
renumber replication files and update README

## (Clean) replication

@@

Run through the files in the following order:

- `re-save-data.R` changes the format of the saved 1-month and 6-month data versions from Stata 13 .dta files to R .rds format. This can be read much quicker than the Stata format. 
- `setup-model-table.R` encodes all the various pieces of information needed to actually run the models reflected in tables 1 and 2. In the original replication files this is done in bits and pieces in `+master.R`, `code/[1|6]mo_define_models.R`, and each model runner file, e.g. `code/1mo_run_escalation.R`. The primary output are several files written to the `output/model-definitions` folder. More details on this below.
- `model-runner.R` runs the models. Adjust the number of WORKERS at the top of the script as needed based on the number of cores on your computer. The primary output of this script is `output/model-table-w-results.csv` and `output/all-predictions.R`.
- `recreate-tables.R` recreates the original and non-smooth ROC versions of Tables 1 and 2 using `output/model-table-w-results.csv` and `output/all-predictions.R`.
- `recreate-figure1.R` recreates the ROC curves in B&S Figure 1 using `output/model-table-w-results.csv` and `output/all-predictions.R`.

In addition, there are some ancillary materials.

- [replication-check.md](replication-check.md) compares the AUC-ROC results we obtain when using smoothed ROC curves to the original B&S results (hand-copied from the paper). When taking into account the implementation fixes we made for two models, and RNG seed variation, we are able to replicate the original results/patterns. 
- [variance.md](variance.md) examines how much the AUC-ROC results vary when you don't set an RNG seed. For the base specification escalation model, the variance is significantly below 0.01, and small changes in the Table 1 and 2 replications mainly occur when the distribution straddles a threshold used for rounding, e.g. 0.825. 
- `make-original-tables.R` is a by-hand coding of the values reported for Tables 1, 2, and 4 in B&S 2020. 
- `rep-check.R` compares the results of our modified replication to the original values reported in Tables 1 and 2 of the B&S paper.

>>>>

## Reproducing our replication

@@

The file numbering indicates the order in which files should be run, and correspond to the steps above. Files with the same number can be run in any order, as long as lower number files have already been run.

Setup:

- `0-packages.R` makes sure all required R packages are installed.

Preparing data for model estimation:

- `1-re-save-data.R` changes the format of the saved 1-month and 6-month data versions from Stata 13 .dta files to R .rds format. This can be read much quicker than the Stata format. 
- `1-make-original-tables.R` is a by-hand coding of the values reported for Tables 1, 2, and 4 in B&S 2020. 
- `1-setup-model-table.R` encodes all the various pieces of information needed to actually run the models reflected in tables 1 and 2. In the original replication files this is done in bits and pieces in `+master.R`, `code/[1|6]mo_define_models.R`, and each model runner file, e.g. `code/1mo_run_escalation.R`. The primary output are several files written to the `output/model-definitions` folder. More details on this below.

Estimate all models (this is where the heavy lifting takes places):

- `2-model-runner.R` runs the models. Adjust the number of WORKERS at the top of the script as needed based on the number of cores on your computer. The primary output of this script is `output/model-table-w-results.csv` and `output/all-predictions.R`.

Process results; figures, tables, etc.:

- `3-...`: the various scripts starting with "3-" recreate the various tables and figures that end up in the paper. These are written to the `rep_nosmooth/output` folder here; the `paper/` folder includes a `update-inputs.R` script that will copy needed pieces over to that folder.

In addition, there are some ancillary materials that are not required for replicating the results in the paper, but add additional information. These are easiest to read in GitHub.

- [replication-check.md](replication-check.md) compares the AUC-ROC results we obtain when using smoothed ROC curves to the original B&S results (hand-copied from the paper). When taking into account the implementation fixes we made for two models, and RNG seed variation, we are able to replicate the original results/patterns. 
- [variance.md](variance.md) examines how much the AUC-ROC results vary when you don't set an RNG seed. For the base specification escalation model, the variance is significantly below 0.01, and small changes in the Table 1 and 2 replications mainly occur when the distribution straddles a threshold used for rounding, e.g. 0.825. 
- `rep-check.R` compares the results of our modified replication to the original values reported in Tables 1 and 2 of the B&S paper.
